Visual Search and Pre-crastination

### 2023-08-31 analysis/1_processing.Rmd
Finished data processing (for now?)

```{r}
dat %>% 
  group_by(person, site) %>%
  summarise(
    sensible = sum(choice == "sensible"),
    pre_crastinate = sum(choice != "sensible")) %>%
  mutate(
    classification = case_when(
      sensible > 4 ~ "no",
      sensible < 3 ~ "yes",
      TRUE ~ "intermediate"),
    classification = as_factor(classification),
    classification = fct_relevel(classification, 
                                 "no", "intermediate", "yes")) %>%
  select(person, site,
         n_pc = pre_crastinate, 
         pre_crastinate = "classification") %>%
  full_join(dat_shls) -> dat

@@

d_out2 <- full_join(d_out, d %>% rename(person = "person")) %>%
  select(-c(LocationLatitude, LocationLongitude, 
            ResponseId, Finished, Duration_in_Seconds, `Duration (in seconds)`,
            StartTime, EndTime))

>>>>

```{r}
dat %>% 
  group_by(person, site) %>%
  summarise(
    sensible = sum(choice == "sensible"),
    pre_crastinate = sum(choice != "sensible"),
    .groups = "drop") %>%
  mutate(
    classification = case_when(
      sensible > 4 ~ "no",
      sensible < 3 ~ "yes",
      TRUE ~ "intermediate"),
    classification = as_factor(classification),
    classification = fct_relevel(classification, 
                                 "no", "intermediate", "yes")) %>%
  select(person, site,
         n_pc = pre_crastinate, 
         pre_crastinate = "classification") -> dat_pc

@@

dat <- full_join(dat_p2, dat_pc)

write_csv(dat, "scratch/prcrastination_and_personality.csv")
